biological data preperation

### 2018-09-18 src/biological_data_prep.Rmd
updated to use new cell id layer

Load the env. data
```{r}
library(raster)
cell_layer <- raster("../output/env/unique_cell.tif") #this is loading the cell layer that was created and saved as a tif
plot(cell_layer)
```
and just grab the attributes of the cell_layer
```{r}
cell_layer
```

>>>>

Load the env. data
```{r}
library(raster)
cell_layer <- raster("../output/env/glo_unique_cell.tif") #this is loading the cell layer that was created and saved as a tif
plot(cell_layer)
```
and just grab the attributes of the cell_layer
```{r}
cell_layer
```
